---
title: 'STAT 147 | HW #4'
author: "Rachna Rawalpally"
subtitle: Matrices, data frames, and R packages
output:
  pdf_document:
    toc: yes
    toc_depth: '2'
  html_document:
    toc: yes
    toc_depth: 2
    number_sections: no
    toc_float:
      collapsed: no
      smooth_scroll: no
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, error = TRUE)
library(tidyverse)
library(magrittr)
library(stringr)
library(ggplot2)
```


```{r}
# You may or may not need to change the path to this file.
# You may or may not need to change the chunk options for this code chunk.
load("murder_weapons.RData")
```

********



# Questions

## Question 1: The Ballroom


| Material |    Price per Pound  | 
|----------|---------------------|
| Pewter   | $4.00               | 
| Brass    | $1.30               | 
| Gold     | $30,735.00             | 
| Silver   | $206.00             | 
| Iron     | $0.07               | 



1. **(10 pts total)** Complete the following using the `candles` data set:
<br><br>
\ \ \ \ (i)   Using functions from the dplyr (and possibly magrittr) package, complete the following.  
\ \ \ \ \ \ (a) **(3 pts)** Create a new column named `Value_Class`.  Make the values inside equal `"precious"` if the material is either gold or silver, and `"regular` otherwise.

\ \ \ \ \ \ (b) **(1 pt)** Creat a NEW column named `Price_Per_Lbs` and assign the monetary values from the table above.  

\ \ \ \ \ \ (c) **(1/2 pts)** Group the data frame by the `Value_Class` column.
\ \ \ \ \ \ (d) **(2 pts)** Calculate a group summary for the average price of each group.  Name the summary column `Average_Price`.  Report the average for each group.
################
\ \ \ \ \ \ (e) **(1/2 pts)** Ungroup the `candle` data frame.
<br><br>
\ \ \ \ (ii) **(2 pts)**  Filter the data `candle` data frame to only contain the precious metals.  Assign the result to a variable named `bling`. 
\ \ \ \ \ \ (a) **(1 pts)** Use the summary function to find the total weight of the precious metals.  Name the summary column `Total_Weight`.  Report the total weight.


ADD ANY CODE CHUNKS TO ANSWER THE ABOVE QUESTIONS BELOW THIS LINE
```{r}
###Q.1.i.a
#'candles' becomes the result of the following 
candles <-
  #start with candles, and then 
  candles %>%
  #replace the values in the column that have FALSE with precious 
  mutate(Value_Class = if_else(str_detect(Material, pattern = "Gold|Silver"),
                               "precious",
                               "regular"))
candles
```
```{r}
###Q.1.i.b
candles <-
#sets the data and then
candles %>%
#adds a new column with the given numbers 
 mutate(Price_Per_Lbs= c(4.00, 1.30, 30735.00, 206.00, 0.07))
#print to check
candles
```
```{r}
###Q.1.i.c
#candles becomes the result 
candles <-
  #starts with candles and then 
  candles %>%
  #build groups around the values in that column 
  group_by(Value_Class)
#print to check
groups(candles)
```
```{r}
###Q.1.i.d
#sets the data and then
candles %>%
  #groups the data by that column
  group_by(Value_Class) %>%
  #summarises the data to get the mean of those columns
  summarise(Average_Price = mean(Price_Per_Lbs))
#average price of precious is $15470.50
#average price of regular is 1.79
```
```{r}
###Q.1.i.e
#starts with candles 
candles <-
  #sets candles and then
candles %>%
  #un groups the column 
ungroup(Value_Class)

#print to check
candles 
```
```{r}
###Q.1.ii
bling <-
  #sets candles and then 
  candles %>%
  #filters data frame to only include precious metals 
   filter(candles == "precious" )
#print to check
bling
```
```{r}
###Q.1.ii.a
#find the total weight of the precious metals 
Total_Weight <-sum(candles$Weight)
#print to check
Total_Weight
```


***  
## Question 2: The Billiard Room


2. **(11 pts total)** Complete the following using the `knife` data set:
<br><br>
\ \ \ \ (i)  **(2 pt)** Remove the columns that begin with `ZScore`.
<br><br>
\ \ \ \ (ii) **(2 pt)** Identify the unique values in all of the columns containing character class variables (with the exception of `Financial Year`.
<br><br>
\ \ \ \ (iii) **(1.5 pt)** Make the column `Financial Quarter` into a factor class variable.  
\ \ \ \ \ \ (a) **(1 pt)** Make sure the levels of the factor variable are in the proper order, Q1, Q2, Q3, Q4.  If they are not in the correct order, please make them so.
<br><br>
\ \ \ \ (iv) **(2 pt)** How many times does each region occur in the data set?
<br><br>
\ \ \ \ (v) **(1 pt)** How many incidents did each force report in the data set (**HINT:** They all reported the same number of times)?
<br><br>
\ \ \ \ (vi) **(1.5 pt)** Refer to part (iv). How many forces are in the region that has the most observations?


ADD ANY CODE CHUNKS TO ANSWER THE ABOVE QUESTIONS BELOW THIS LINE

```{r}
###Q.2.i
#sets the data equal to  
knife <-
  #sets the data and then
  knife %>%
  #gets rid of columns that start with ZScore 
  select(-starts_with("ZScore"))
#print the names of the new column 
names(knife)
```
```{r}
###Q.2.ii
#gets the variables that are character variables
sapply(knife,class)
#gets the unique values for this column 
unique(knife$`Force Name`)
#gets the unique columns for this column 
unique(knife$Region)
#gets the unique columns for this column
unique(knife$`Financial Quarter`)
```
```{r}
###Q.2.iii
#changes the class the factor 
knife$`Financial Quarter` <- as_factor(knife$`Financial Quarter`)
#checks the class 
class(knife$`Financial Quarter`)
```
```{r}
###Q.2.iii.a
#sets the column to factor and in order
levels(knife$`Financial Quarter`) <- c("Q1", "Q2", "Q3", "Q4")
knife %$% 
  levels(`Financial Quarter`)
```
```{r}
###Q.2.iv
#amount of times region occurs in the data set 
knife %>%
  group_by(Region) %>%
  summarise(counts = n())
```
```{r}
###Q.2.v
#amount of incidents in force report
knife %>%
  group_by(`Force Name`) %>%
  summary(counts = n ()) %>%
  unique(counts)
#44
```
```{r}
###Q.2.vi
#sets the data equal to 
region <- 
  #sets the data and then 
  knife %>%
  #filters the data to only include regions in the east 
  filter(Region == "East")
#counts the forces that are in that region 
unique(region$`Force Name`)
#6
```


***  

## Question 3: The Conservatory


3. **(10 pts total)** Using pipe operators to build a **single, continuous sequence of instructions**, complete the following using the `chop_chop` data set.  Be sure to comment each step clearly:
<br><br>
\ \ \ \ (i)  **(1 pt)** Make the `type` column "Title Case".
<br><br>
\ \ \ \ (ii)  **(1 pt)** Make the `origin` column "UPPER CASE".
<br><br>
\ \ \ \ (iii)  **(2 pt)** Create a new column called `murica` that detects if the `origin` column references the Americas.
<br><br>
\ \ \ \ (iv)  **(2 pt)** Reorganize the columns such that `murica` comes first, `origin` comes second and `type` comes last.
<br><br>
\ \ \ \ (v)  Sort the rows of `chop_chop`  
\ \ \ \ \ \ (a) **(1 pt)** First by `murica` such that `TRUE` is on top and `FALSE` is below.  
\ \ \ \ \ \ (b) **(1.5 pt)** Then, within those groups, sort by `type` in ascending order.
<br><br>
\ \ \ \ (vi)  **(1/2 pt)** Group the data frame by the values in the logical column created in part (iii).
<br><br>
\ \ \ \ (vii)  **(2 pt)** Create a new column named `counts` which contains the number of rows/observations within each group (without using the `summarise()` function).


ADD ANY CODE CHUNKS TO ANSWER THE ABOVE QUESTIONS BELOW THIS LINE

```{r}
###Q.3.i
#sets the data 
chop_chop <-
  #sets the data and then 
  chop_chop %>%
  #changes the name of the column
  mutate(type = str_to_title(type))
#print to check
chop_chop
```
```{r}
###Q.3.ii
#sets the data equal to 
chop_chop <-
  #pulls the data and then 
  chop_chop %>%
  #changes the column to all upper case 
  mutate(origin = str_to_upper(origin))
#print to check
chop_chop
```
```{r}
###Q.3.iii
#sets the data equal to 
chop_chop <-
  #sets the data and then  
  chop_chop %>%
  #creates new column that contains detects america
  mutate(murica = str_detect(string = origin, pattern = "AMERICA")) %>%
  #create the column in the data frame 
  select(murica, everything())
#print to check
chop_chop
```
```{r}
###Q.3.iv
#sets the data and then 
chop_chop %>%
  #sets the column order 
  select(murica, origin, type)
```
```{r}
###Q.3.v.a
#sets the data frame 
chop_chop <-
  #sets the data and then 
  chop_chop %>%
  #arranges the data from descending order 
  arrange(desc(murica))
  #prints to check
  chop_chop
```
```{r}
###Q.3.v.b
#sets the data equal to 
chop_chop <-
  #sets the data and then
  chop_chop %>%
  #arranges the data in order of type
  arrange(type) %>%
  #and the arranges the data of that column in order of descending 
  arrange(desc(murica))
#print to check
chop_chop
```
```{r}
###Q.3.vi
#sets the data frame 
chop_chop <-
  #sets the data and then 
  chop_chop %>%
  #groups the data 
  group_by(murica)
```
```{r}
###Q.3.vii
#gets the data and then 
chop_chop %>%
  #groups the data by the column
  group_by(murica) %>%
  #counts the number of observations
  add_count()

```

***


## Question 4: The Dining Room


4. **(20 pts total)** Complete the following using the `bang_bang` data set: 
<br><br>
\ \ \ \ (i)  **(1/2 pt)** Select the columns as follows:  
\ \ \ \ \ \ (a) **(3.5 pt)** Keep the `state` column and all columns that start with "private", "redemption", or "return". 
\ \ \ \ \ \ (b) **(2 pt)** Drop all any remaining columns if they end with "other".  
<br><br>
\ \ \ \ (ii)  **(1/2 pt)** Read about the `complete.cases()` function.  
\ \ \ \ \ \ (a) **(1/2 pt)** From which package does this function originate? 

\ \ \ \ \ \ (b) **(2 pt)** Use this function to remove ALL rows that contain ANY missing (`NA`) values.   
\ \ \ \ \ \ (d) **(1 pt)** How many observations remain after removing those rows? 
\ \ \ \ \ \ (c) **(1 pt)** How many rows had at least one missing (`NA`) value?
<br><br>
\ \ \ \ (iii)  **(2 pt)** How many observations are there for each state (**HINT**: Each state occurs the same number of times!)
<br><br>
\ \ \ \ (iv)  **(1 pt)** Use the exposition pipe operator to plot `private_sale_handgun` (x) vs `private_sale_long_gun` (y).
<br><br>
\ \ \ \ (v)  **(2 pt)** Use the `lm()` function to fit a linear gression, using `private_sale_handgun` as the independent (x) variabe, and `private_sale_long_gun` as the dependent (y) variable. 
\ \ \ \ \ \ (a) **(1/2 pt)**  store the linear model to a variable named `gun_lm`. 
\ \ \ \ \ \ (b) **(1.5 pt)**  Use the appropriate function(s) to obtain the model estimates and the (Multiple) R-Squared value.  
\ \ \ \ \ \ (c) **(3 pt)** In a separate code chunk, replot `private_sale_handgun` (x) vs `private_sale_long_gun` (y) and draw a red, deshed line over it using the `gun_lm` variable. Adjust the code chunk options so that the code does not show up when you knit the document, but the plot does.



ADD ANY CODE CHUNKS TO ANSWER THE ABOVE QUESTIONS BELOW THIS LINE

```{r}
###Q.4.i.a
#sets the data equal to 
bang_bang <-
  #sets the data and then
  bang_bang %>%
  #keeps the columns starting with the column names
  select(starts_with("private_"),starts_with("redemption_"), 
         starts_with("return_"), state)
#checks to names of the columns in the data frame 
names(bang_bang)
```
```{r}
###Q.4.i.b
#sets equal to 
bang_bang <-
  #sets the data and then 
  bang_bang %>%
  #gets rid of columns ending with other 
  select(-ends_with("_other"))
#checks to make sure the columns are gone 
names(bang_bang)
```
###Q.ii.a
#it is from the R stats package 
```{r}
###Q.4.ii.b
#function locates all the rows missing NA
bang_bang <- filter(complete.cases(.))
#gets rid of the all of rows missing NA
bang_bang
```
```{r}
###Q.4.ii.d
#gives the dimesions of the data frame 
nrow(bang_bang)
#3135 observations 
```
```{r}
###Q.4.ii.c
#counts the rows missing an NA
nrow(bang_bang)
#0
```
```{r}
###Q.4.iii
#sets the function and then
bang_bang %>%
  #group the function by column
  group_by(state) %>%
  #count the amount of observations 
  summarise(count = n()) $#$
  unique(n)
#57
```
```{r}
###Q.4.iv
#sets the function and then
bang_bang %$%
  #plots the function
  plot(private_sale_handgun, private_sale_long_gun)
```
```{r}
###Q.4.v
#function to fit a linear regression
lm(formula = private_sale_long_gun ~ private_sale_handgun, 
   data = bang_bang)
```
```{r}
###Q.4.v.a
#sets the linear regression function equal to a new variable 
gun_lm <- lm(formula = private_sale_long_gun ~ private_sale_handgun, 
   data = bang_bang)
```
```{r}
###Q.4.v.b
##sets the linear regression function equal to a new variable 
gun_lm <- lm(formula = private_sale_long_gun ~ private_sale_handgun, 
   data = bang_bang)
#summary function to find model estimates
summary(gun_lm)
```
```{r}
###Q.4.v.c
#sets the data and then 
bang_bang %$%
  #plots the data 
  plot(private_sale_handgun, private_sale_long_gun)
#uses the data to create a line in teh graph 
#the line is red and dashed 
abline(gun_lm,
       col = "red",
       lty = 2)
```

***  

## Question 5: The Hall


5. **(9 pts)** Complete the following using the `ntrl_rope` and `synth_rope` data sets.  Feel free to use the [`stringr` cheat sheet](https://evoldyn.gitlab.io/evomics-2018/ref-sheets/R_strings.pdf). 
<br><br>
\ \ \ \ (i)  **(1 pt)**  For the natural rope, modify the `Material` to "Title Case".
<br><br>
\ \ \ \ (ii)  **(1 pt)**   For the synthetic rope, modify the `Material` to "lower case".
<br><br>
\ \ \ \ (iii)  **(1 pt)**  Combine the two data frames in to a new data frame named `all_rope`.
<br><br>
\ \ \ \ (iv)  **(2 pt)**   Filter the rows such that the `Material` column contains at least one "y" in the name. Then arrange the rows by the `Length` column.
<br><br>
\ \ \ \ (v)  **(4 pt)** Create a new column named `name_len` which contains the number of letters in the `Material` column.  Then, find the average name length for each `Type`. 


ADD ANY CODE CHUNKS TO ANSWER THE ABOVE QUESTIONS BELOW THIS LINE

```{r}
###Q.5.i
#changes the column names to all title names
ntrl_rope$Material = str_to_title(ntrl_rope$Material)
#print to check
ntrl_rope
```
```{r}
###Q.5.ii
#changes the column names to all lower
synth_rope$Material = str_to_lower((synth_rope$Material))
#print to check
synth_rope
```
```{r}
###Q.5.iii
#combine the data frames 
all_rope <- rbind(ntrl_rope, synth_rope)
#print to check
all_rope
```
```{r}
###Q.5.iv
#sets the data equal to 
all_rope <-
  #sets the data and then
  all_rope %>%
  #filter the data to only include one y
  filter(str_detect(string = Material, pattern = "y")) %>%
  #arrange the lengths by descending order
  arrange(desc(Length))
#print to check
all_rope
```
```{r}
###Q.5.v
all_rope %>%
#gets the number of character for each column
  mutate(name_len = str_length(Material)) %>%
#binds the columns together
  group_by(Type) %>%
#gets the mean of the column
  summarise(avg_name_len = mean(name_len))
```
***  


## Question 6: The Kitchen


6. **(12 pts)** Complete the following.  Feel free to use the [R Markdown cheat sheet](https://rstudio.com/wp-content/uploads/2015/02/rmarkdown-cheatsheet.pdf). 
<br><br>
\ \ \ \ (i) Google the term `u can't touch this lyrics`.  
\ \ \ \ \ \ (a) **(1.5 pt)** Using rmakdown syntax, create an un-ordered list of the first four lines of the lyrics to the song.  
\ \ \ \ \ \ (b) **(1.5 pt)**  Using rmakdown syntax, continue the above un-ordered list with subitems for the next four lines (lines 5 through 8) of lyrics.  
\ \ \ \ \ \ (c) **(2 pt)**  Using rmakdown syntax, add the next four lines (lines 9 through 12) of lyrics in a `block-quote`. Make sure each lyric line shows up on it's own line in the final knitted document.
<br><br>
\ \ \ \ (ii) Complete the following using the `hammer_time` data set:  
\ \ \ \ \ \ (a) **(2 pt)** In a single chain of piped instructions, convert the `chart_position` column of the `hammer_time` data frame to be `numeric`, then filter out the missing value. 
\ \ \ \ \ \ (b) **(1 pt)** Calculate the mean chart position of the remaining 5 songs.
\ \ \ \ \ \ (c) **(3 pt)** Use **in-line `R` code** to write a sentence which reports the average chart position of the remaining 5 songs.
<br><br>
\ \ \ \ (iii)  **(1 pt)** Filter the data frame to only contain the songs that made it into the top 10 chart positions.
<br><br>


###Q.6.i.a and ###Q.6.i.b

* You can't touch this
* You can't touch this
* You can't touch this
* You can't touch this
  + My, my, my my music hits me so hard
  + Makes me say, "Oh my Lord"
  + Thank you for blessin' me
  + With a mind to rhyme and two hype feet


####Q.6.i.c

> It feels good, when you know you're down

> A super dope homeboy from the Oaktown

> And I'm known as such

> And this is a beat, uh you can't touch.

```{r}
###Q.6.ii.a
#sets the data equal to
hammer_time <-
  #sets the data and then
  hammer_time %>%
  #filter to not include the missing value
  filter(chart_position != ".")
#change class to numeric
  hammer_time$chart_position <- as.numeric(hammer_time$chart_position) 
#print to check
hammer_time
#check class
class(hammer_time$chart_position)
```
```{r}
###Q.6.ii.b
#gets the mean of the chart position
mean(hammer_time$chart_position)
#32.8
```


###Q.6.ii.c

The average chart position of the remaining 5 songs is 
`r mean(hammer_time$chart_position)`.

ADD ANY ADDITIONAL CODE CHUNKS TO ANSWER THE ABOVE QUESTIONS BELOW THIS LINE

```{r}
###Q.6.iii
#sets the data equal to 
hammer_time <-
  #sets the data and then 
  hammer_time %>%
  #filter the data to only include equal or greater than 10
  filter(chart_position <= 10)
#print to check
hammer_time
```

***  


 
## Question 7: The Library



7. **(16 pts)** Complete the following using the `bottles` data set: 
<br><br>
Note that there is a problem with the `price` column:  While it represents price (a numeric value) the class of that column is `character`.  This is because some of the values have a comma `,` or `$`  in them in them, while others actually have entire words (for instance, `$15,000 or $60,000/set`).
<br><br>
\ \ \ \ (i)    In a single sequence of piped commands:  
\ \ \ \ \ \ (a) **(3 pts)** Read the documentation for `str_detect()` and use it to filter out the rows in the bottles data frame for which `price` that contain a forward slashe "`/`".  
\ \ \ \ \ \ (b) **(4.5 pts)** Use the `str_remove()` function to take any commas out of the `price` column.  (**We DON'T want to remove those rows!**  Instead, we want to remove those COMMAS and leave the rest of the price as-is.)  
\ \ \ \ \ \ (c) **(1 pts)** Convert the price column to a numeric variable. 
\ \ \ \ \ \ (d) **(2 pts)** Place the `price` and `review_points` column on the left side of the data frame, and then keep all other columns to the right.
<br><br>
\ \ \ \ (ii) **(2 pts)** Use the exposition pipe operator to plot `price` vs `review_points`.
<br><br>
\ \ \ \ (iii) **(3.5 pts)** Use the exposition pipe operator to plot `price` vs `review_points` with both variables on a log scale **WITHOUT** using the `log()` function.



ADD ANY CODE CHUNKS TO ANSWER THE ABOVE QUESTIONS BELOW THIS LINE

```{r}
###Q.7.i.a
#sets the data equal to 
bottles <-
  #sets the data and then 
  bottles %>%
  #filter the data to get rid of forward slash
  mutate(price = str_remove_all(string = price, pattern = "/"))
#print to check
bottles
```
```{r}
###Q.7.i.b
#sets the data equal to 
bottles <-
  #sets the data and then
  bottles %>%
  #removes all of the commas in that column
  mutate(price = str_remove_all(string = price, pattern = "[,]"))
#print to check
bottles
```
```{r}
###Q.7.i.c
#convert the column to numeric
bottles$price <- as.numeric(bottles$price)
#checks the class
class(bottles$price)
```
```{r}
###Q.7.i.d
#sets the data equal to 
bottles <-
  # sets the data and then
  bottles %>%
  #Select the data to arrange the columns in a specific order 
  select(price, review_point, everything())
#print to check
bottles
```
```{r}
###Q.7..ii
#sets the data using the exposition pipe operator
bottles %$%
  #plots the data 
  plot(price, review_point)
```
```{r}
###Q.7.iii
#sets the data and then
bottles %$%
  #plots the data using log scale  
  plot(x= price, y= review_point, log = "xy")
```


***  

 
## Question 8: The Lounge


8. **(13 pts total)** Complete the following using the `pipes` data set: 
<br><br>
How many addresses show up three or more times??  List them in order of counts, and alphabetically within each count group.



ADD ANY CODE CHUNKS TO ANSWER THE ABOVE QUESTIONS BELOW THIS LINE

```{r}
###Q.8
#sets the data frame to only include addresses
n_occur <- data.frame(table(pipes$Full_Address))
#sets new data frame to only contain addresses greater or equal to 3
New_address <- pipes[pipes$Full_Address %in% n_occur$Var1[n_occur$Freq >= 3],]
#sets the data and then
New_address %>%
  #group the data by the column and then 
  group_by(Full_Address) %>%
  #summarize the data and count and then
  summarise(counts = n()) %>%
  #arranges the data in order of count and alphabetically 
  arrange(desc(counts), order(Full_Address))

```

***  


## Question 9: The Study


9. **(14 pts)** Complete the following using the `wrenches` data set:
<br><br>
\ \ \ \ (i) **(2 pt)** Filter out the rows for which there are missing (`NA`) values in the `British/Commonwealth name` column.
<br><br> 
\ \ \ \ (ii) **(2 pt)** How many wrenches fall into each `Group` catergory??
<br><br> 


\ \ \ \ (iii) **(3 pts)**  How many wrenches have the same name in both countries?  Subset the data frame to just those rows using only the `filter()` function.
<br><br>
\ \ \ \ (iv) **(3 pts)** How many wrenches/spanners do not have an identified name in the `British/Commonwealth name` column?
<br><br>
\ \ \ \ (v) Some of the tools have an animal name in them.  Those names are one of the following: `monkey`, `crow`, `spider`, `dog`, or `alligator`.  
\ \ \ \ \ \ (a) **(1 pts)** How many American wrench names contain an animal name?
\ \ \ \ \ \ (b) **(1 pts)** How many British wrench names contain an animal name?
<br><br>
\ \ \ \ (vi) In the UK, the common name for a wrench is a "spanner".  
\ \ \ \ \ \ (a) **(1 pts)** How many British wrench names contain the word "spanner"?
\ \ \ \ \ \ (b) **(1 pts)** How many American wrench names contain the word "spanner"?
ADD ANY CODE CHUNKS TO ANSWER THE ABOVE QUESTIONS BELOW THIS LINE

```{r}
###Q.9.i
#sets the data
wrenches <-
  #uses the data and then 
  wrenches %>%
  #filters to not include missing NA
  filter(`British/Commonwealth name` != "NA")
#print to check
wrenches
```
```{r}
###Q.9.ii
#sets the data and then
wrenches %>%
  #groups the data by Group column
  group_by(Group) %>%
  #counts the data 
  summarise(count = n())
```
```{r}
###Q.9.iii
  #uses this data set and then 
  wrenches %>%
  #filters the data set to only the rows that follow the logical comparison
  filter(`American name` == `British/Commonwealth name`)
#print to check
wrenches
#3
```
```{r}
###Q.9.iv
  #uses this data set and then 
  wrenches %>%
  #filters the data set to only the rows that follow the logical comparison
  filter(`British/Commonwealth name` == "?") %>%
  nrow()
#print to check
wrenches
#10
```
```{r}
###Q.9.v.a
#the rows with contains that word 
grep("monkey",wrenches$`American name`)
#the rows with contains that word 
grep("crow", wrenches$`American name`) 
#the rows with contains that word 
grep("spider", wrenches$`American name`)
#the rows with contains that word 
grep("dog", wrenches$`American name`) 
#the rows with contains that word 
grep ("alligator", wrenches$`American name`) 
#6
```
```{r}
###Q.9.v.b
#the rows with contains that word 
grep("monkey",wrenches$`British/Commonwealth name`)
#the rows with contains that word 
grep("crow", wrenches$`British/Commonwealth name`) 
#the rows with contains that word 
grep("spider", wrenches$`British/Commonwealth name`)
#the rows with contains that word 
grep("dog", wrenches$`British/Commonwealth name`) 
#the rows with contains that word 
grep ("alligator", wrenches$`British/Commonwealth name`) 
#2
```
```{r}
###Q.9.vi.a
#shows how many wrenches in that column cotain that word
length(grep("spanner", wrenches$`British/Commonwealth name`))
#18
#or
wrenches %>%
  filter(str_detect(`British/Commonwealth name`, pattern = "spanner"))
```
```{r}
###Q.9.vi.b
#shows how many wrenches in that column contain that word
length(grep("spanner", wrenches$`American name`))
#1
```


****
<p style="font-size:30px;color:#003DA5">
<b>Congratulations!</b>  You've completed the assignment.
<br><br>
Please be sure to upload the completed HW's:  
\ \ \ 1. `.Rmd` file  
\ \ \ 2. `html` file <br>
to the online submission form.
</p>


















